Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 3 updates

When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case). The stellar activity correction we propose can therefore be written as:
%
\begin{equation}
RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}. 
\xavier{This interaction term can accounts for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that the two variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
}. \xavier{Umberto, Jessi, is this correct ?} \jessi{I modified the statement - is the modification clear?}
%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

>>>>

When fitting for planetary signals in RV data, it is common to include linear dependencies with the BIS SPAN and the FWHM and to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
We propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case). The stellar activity correction we propose can therefore be written as:
%
\begin{equation}
RV_{\text{activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the error with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
The contrast parameter $A$ accounts for the presence of a spot on the stellar surface, which produces a change in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
The benefits of including a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better understood through the results of the examples presented in Sec.\ref{sec:soap}. 
This interaction term can account for possible interactions between SN FWHM (or FWHM) and $\gamma$ (or BIS SPAN), meaning that each  variables' association with the response, $RV_{\text{activity}}$, depends also on the other variable.
%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.
